### 2023-10-31 chapters/introduction.tex
Update thesis scope and outline

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.55\textheight]{kushim_multiplication.png}
    \caption[Technology is difficult. The accountant Kushim made mistakenly claimed $5 \times \sfrac{1}{2} = 5$.]{ Technology is difficult. Between 3400 and 3000 BCE, the Sumerian accountant Kushim wrote this tablet. Besides calculations of basic ingredients required for the production of cereal products, in the top left $6 \times 2$ grid it contains a multiplication table. While presumably aimed to ease the strenuous work of doing Sumerian mathematics, unfortunately, the top row states: $5 \times \sfrac{1}{2} = 5$, an unforgiving imprint the worlds first recorded mathematical error \parencite{nissen_archaic_1993, renn_learning_2019}, \parencite[photo credit][]{cuneiformdigitallibraryinitiativecdli_msvo_2018}.}
    \label{fig:kushim_multiplication}
\end{figure}
\todo[inline]{\cref{fig:kushim_multiplication} is awaiting response from CDLI with proper reference to tablet.}

@@

\subsection{Model calibration} \label{subsec:model-calibration}
% 
The problem of miscalibration in machine learning models is well-known and has been studied for decades \parencite{lewis_sequential_1995, platt_probabilistic_1999, garczarek_classification_2002, zadrozny_transforming_2002, bennett_using_2003, niculescu-mizil_predicting_2005}. One of the best known methods for calibrating a binary classifier is Platt scaling which fits a logistic regression model to the model outputs, assuming that the miscalibration can be corrected by a logarithmic function \parencite{platt_probabilistic_1999}. Another method is isotonic regression which instead fits a nonparametric, monotonic function \parencite{zadrozny_transforming_2002}. 
More recently, \textcite{guo_calibration_2017} proposed a single-parameter variant of Platt-scaling that fits only a temperature parameter on the logits of a neural network classifier. 
These methods are generally simple and effective, but not without limitations. 
To perform the calibration, most of the methods require a held-out validation set on which the model was not trained, Platt scaling and isotonic regression are not naively applicable to multi-class classification problems, and how to calibrate models for structured prediction tasks, such as speech recognition and machine translation, remains an open problem \parencite{astudillo_uncertainty_2010, astudillo_integration_2013, jayashankar_detecting_2020}.

@@

This introduction provided a high-level overview of the motivation behind the research project by focusing on the use-cases of stroke recognition and automated medical coding as well as speech processing and the importance of uncertainty quantification. 
The remainder of \cref{part:background} consists of two chapters. 
\Cref{chp:main-contributions} presents the research hypotheses and contributions of the thesis via the included papers. 
\Cref{chp:technical-background} provides relevant technical background to the included papers, including uncertainty, out-of-distribution detection, and variational autoencoders.

\Cref{part:unsupervised-uncertainty-estimation,part:unsupervised-speech-representation-learning,part:medical-applications} contain a number of chapters that each correspond to a primary paper. 
\Cref{part:unsupervised-uncertainty-estimation} is made up of three papers on variational autoencoders and their applications to out-of-distribution detection and speech modelling \parencite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. 
\Cref{part:unsupervised-speech-representation-learning} is a single, comprehensive review paper on self"=supervised speech representation learning \parencite{mohamed_selfsupervised_2022}. 
\Cref{part:medical-applications} consists of two papers on applications of machine learning within the medical domain, specifically recognition of stroke cases in calls to medical helplines \parencite{wenstrup_retrospective_2023} and medical coding of clinical notes \parencite{edin_automated_2023}.

Finally, \cref{part:discussion-and-conclusion} concludes the thesis by discussing the presented work and presenting future directions for research.

>>>>

\begin{figure}[t]
    \centering
    % \includegraphics[width=0.90\textwidth]{plimpton_322.png}
    \includegraphics[height=0.55\textheight]{kushim_multiplication.png}
    \caption[Technology is difficult. The accountant Kushim made mistakenly claimed $5 \times \sfrac{1}{2} = 5$.]{ Technology is difficult. Between 3400 and 3000 BCE, the Sumerian accountant Kushim wrote this tablet. Besides calculations of basic ingredients required for the production of cereal products, in the top left $6 \times 2$ grid it contains a multiplication table. While presumably aimed to ease the strenuous work of doing Sumerian mathematics, unfortunately, the top row states: $5 \times \sfrac{1}{2} = 5$, an unforgiving imprint the worlds first recorded mathematical error \parencite{nissen_archaic_1993, renn_learning_2019}, \parencite[photo credit][]{cuneiformdigitallibraryinitiativecdli_msvo_2018}.}
    \label{fig:kushim_multiplication}
\end{figure}

@@

\subsection{Model calibration} \label{subsec:model-calibration}
% 
The problem of miscalibration in machine learning models is well-known and has been studied for decades \parencite{lewis_sequential_1995, platt_probabilistic_1999, garczarek_classification_2002, zadrozny_transforming_2002, bennett_using_2003, niculescu-mizil_predicting_2005}. One of the best known methods for calibrating a binary classifier is Platt scaling which fits a logistic regression model to the model outputs, assuming that the miscalibration can be corrected by a logarithmic function \parencite{platt_probabilistic_1999}. Another method is isotonic regression which instead fits a nonparametric, monotonic function \parencite{zadrozny_transforming_2002}. 
More recently, \textcite{guo_calibration_2017} proposed a single-parameter variant of Platt-scaling that fits only a temperature parameter on the logits of a neural network classifier. 
These methods are generally simple and effective, but not without limitations. 
To perform the calibration, most of the methods require a held-out validation set on which the model was not trained, Platt scaling and isotonic regression are not directly applicable to multi-class classification problems, and how to calibrate models for structured prediction tasks, such as speech recognition and machine translation, remains an open problem \parencite{astudillo_uncertainty_2010, astudillo_integration_2013, jayashankar_detecting_2020}.

@@

This introduction provided a high-level overview of the motivation behind the research project by focusing on the use-cases of stroke recognition and automated medical coding as well as speech processing and the importance of uncertainty quantification.

The remainder of \cref{part:background} consists of two chapters. 
\Cref{chp:main-contributions} presents the research hypotheses and contributions of the thesis via the included papers. 
\Cref{chp:technical-background} provides relevant technical background to the included papers, including uncertainty, out-of-distribution detection, and variational autoencoders.

\Cref{part:unsupervised-uncertainty-estimation,part:unsupervised-speech-representation-learning,part:medical-applications} contain a number of chapters that each correspond to a primary paper. 
\Cref{part:unsupervised-uncertainty-estimation} is made up of two papers dealing with out-of-distribution detection using generative models, including variational autoencoders \parencite{havtorn_hierarchical_2021,bergamin_modelagnostic_2022}. 
\Cref{part:unsupervised-speech-representation-learning} consists of two papers that explore speech representation learning with variational autoencoders and self"=supervised methods \parencite{borgholt_brief_2022,havtorn_benchmarking_2022}. 
\Cref{part:medical-applications} consists of two papers on applications of machine learning within the medical domain, specifically recognition of stroke cases in calls to medical helplines \parencite{wenstrup_retrospective_2023} and medical coding of clinical notes \parencite{edin_automated_2023}.

Finally, \cref{part:discussion-and-conclusion} concludes the thesis by discussing the presented work and future directions for research.
